First Workshop on on Sustainable Software for Science: Practice and Experiences (WSSSPE): Submission and Peer-Review Process, and Results

### 2014-01-21 WSSSPE1_report/WSSSPE_pre-meeting_report.tex
fixing latex bug
small fixed - making more past tense

Progress in scientific research is dependent on the quality and accessibility of software at all levels and it is now critical to address many challenges related to the development, deployment, and maintenance of reusable software. In addition, it is essential that scientists, researchers, and students are able to learn and adopt software-related skills and methodologies. Established researchers are already acquiring some of these skills, and in particular a specialized class of software developers is emerging in academic environments who are an integral and embedded part of successful research teams. The WSSSPE workshop is intended provide a forum for discussion of the challenges, including both positions and experiences. The short papers and discussion will be archived to provide a basis for continued discussion, and the workshop is intended to feed into the collaborative writing of one or more journal publications.

>>>>

Progress in scientific research is dependent on the quality and accessibility of software at all levels and it is now critical to address many challenges related to the development, deployment, and maintenance of reusable software. In addition, it is essential that scientists, researchers, and students are able to learn and adopt software-related skills and methodologies. Established researchers are already acquiring some of these skills, and in particular a specialized class of software developers is emerging in academic environments who are an integral and embedded part of successful research teams. The WSSSPE workshop was intended to provide a forum for discussion of the challenges, including both positions and experiences. The short papers and discussion were archived to provide a basis for continued discussion, and the workshop was intended to feed into the collaborative writing of one or more journal publications.
